Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-05-18 paper/paper.tex
typo

\paragraph{The ``dark room'' experiment.}
Since the FEP postulates that all ongoing intelligent behavior in an organism is geared towards reaching the grand goal of minimizing surprisal, an organism which enters a \textit{dark room}\footnote{\textit{Dark} is used here as an allegory to indicate the complete absence of any \textit{external} sensory input.} (Fig. \ref{fig:darkroom}) would strive to remain there as its sensory input would be perfectly predictable in such a state \citep{darkroom2012}.
However, such a tendency is definitely not what is observed, neither in humans nor in animals: if you get into a dark room,
\begin{wrapfigure}{r}{.45\linewidth}
  \centering
  \includegraphics[width=1.\linewidth]{darkroom.jpg}
  \caption{\textbf{The \textit{dark room} experiment.} The adjective \textit{dark} is used as an allegory to indicate the complete absence of any \textit{external} sensory input.}  
  \label{fig:darkroom}
\end{wrapfigure}
you try to figure out where the light switch is, so as to \textit{explore} this mysterious room, or simply get out of it! Defenders of the FEP have retaliated by advancing the `full package''\citep{darkroom2012}: FEP is multi-scale, and there would be a meta-scale at which the organism would
be \textit{surprised} by such a \textit{lack of surprise}. According to this argument, a dark room is thus paradoxically, a state of extremely high surprise. Driven by the zeal to always diminish surprise, the FEP agent would eventually bootstrap itself out of such saddles, to explore more interesting corners of the environment. Recourse to this argument is equivalent to invoking a \textit{halting oracle}\citep{haltingoracle}, an arbitrarily powerful \textit{Turing machine} which can solve the \textit{halting problem} (an arbitrarily difficult computational problem which cannot be solved under any reasonable \textit{model of computation}, not even in principle!). But this is problematic as it sucks up the problem (that of decision-making and active agency) the theory is intends to elude in the first place.

>>>>

\paragraph{The ``dark room'' experiment.}
Since FEP-based theories \citep{friston2010free,fristonAIorRL} postulate that all ongoing intelligent behavior in an organism is geared towards reaching the grand goal of minimizing surprisal, an organism which enters a \textit{dark room}\footnote{\textit{Dark} is used here as an allegory to indicate the complete absence of any \textit{external} sensory input.} (Fig. \ref{fig:darkroom}) would strive to remain there as its sensory input would be perfectly predictable in such a state \citep{darkroom2012}.
However, such a tendency is definitely not what is observed, neither in humans nor in animals: if you get into a dark room,
\begin{wrapfigure}{r}{.45\linewidth}
  \centering
  \includegraphics[width=1.\linewidth]{darkroom.jpg}
  \caption{\textbf{The \textit{dark room} experiment.} The adjective \textit{dark} is used as an allegory to indicate the complete absence of any \textit{external} sensory input.}  
  \label{fig:darkroom}
\end{wrapfigure}
you try to figure out where the light switch is, so as to \textit{explore} this mysterious room, or simply get out of it! Defenders of the FEP have retaliated by advancing the `full package''\citep{darkroom2012}: FEP is multi-scale, and there would be a meta-scale at which the organism would
be \textit{surprised} by such a \textit{lack of surprise}. According to this argument, a dark room is thus paradoxically, a state of extremely high surprise. Driven by the zeal to always diminish surprise, the FEP agent would eventually bootstrap itself out of such saddles, to explore more interesting corners of the environment. Recourse to this argument is equivalent to invoking a \textit{halting oracle}\citep{haltingoracle}, an arbitrarily powerful \textit{Turing machine} which can solve the \textit{halting problem} (an arbitrarily difficult computational problem which cannot be solved under any reasonable \textit{model of computation}, not even in principle!). But this is problematic as it sucks up the problem (that of decision-making and active agency) the theory intends to elude in the first place.
